---
title: "Empirical software engineering"
subtitle: |
  | Lab 1: Descriptive statistics, regression and hypothesis testing
  | Group 9
output:
  pdf_document
author:
  - Anton Lutteman
  - Daniel Olsson
  - Gerson Silva Filho
  - Johan Mejborn
date: "`r format(Sys.time(), '%d %B %Y')`"
---

# Exercise 1 - Time to Develop

## a) Descriptive data:
Mean = `r mean(d1)` \
Median = `r median(d1)` \
Standard deviation = `r sd(d1)` \
Variance = `r var(d1)` \

## b) What is being calculated?
What is being calculated is the **sample** standard deviation, since the company has provided the time 
spent only for 16 features chosen at random. The population would be if we had the time 
for all the features developed.


## c) Hypothesis
The hypothesis is one tailed because we are only looking in one direction. 

**h0**: mean(Time) <= 225 Hours \
**h1**: mean(Time) > 225 Hours

## d) Histogram
```{r histplots, fig.show="hold", out.width="33%"}
dbin<-data.frame(d1)
histogram_with_bin <- function(bin_size) {
  title<- paste("Histogram with Bin size = ", bin_size)
  ggplot(data = dbin, aes(x=d1))+
  geom_histogram(binwidth = bin_size)+
  labs(title=title, x='Time to develop', y='Number of occurences')
}

histogram_with_bin(50)
histogram_with_bin(75)
histogram_with_bin(100)
```

Changing the amount of bins doesn't change the perspective drastically, but we can 
observe that most of the values are concentrated between 200 and 250, using the bin size of 50.
When we used bigger values we would assume that most values were between 100 and 300 which gives
us much less precision on that.


## e) qq-Plot

```{r qqPlot}
car::qqPlot(d1,main = 'qq-Plot Time to Develop', ylab= 'Time to develop')
```

## f) Shapiro-Wilk test

```{r shapiroTest}
shapiro.test(d1)
```
Observing the QQ-plot of the data we can see that it doesn't seem to follow a normal
distribution since the residuals are not independent and there are points out of the 95% confidence interval that we are using in the plot. 

The Shapiro-Wilk would also reinforce this non-normality of the data since it's *W* 
value is below 1, but the p-value is larger than alpha so we can't reject that the data is normally distributed based on this test.

## g) One sample T-Test

We are using a T-Test instead of a Z-Test because we have a sample size smaller than 30
and we don't know the standard deviation of the population. We used a one sample T-Test since we have only one sample group in this experiment.

The data follows the assumptions of a T-Tests since:\
* It follows a continuous scale
* We assumed that the data was collected randomly from the population
* We assumed that the data is approximately normally distributed since we couldn't reject it using the Shapiro-Wilk test.

```{r ttest}
t.test(d1, mu=225 , alternative = 'greater' ,conf.level=0.95)
```

As seen in the test output the confidence interval is between 208 to infinity.

Based on the T-Test we can't reject the null hypothesis that the time to develop is
less than 225 because the p-value is larger than the alpha value.


# Exercise 2 - Performance

## a) Descriptive Statistics
```{r desc_statistics}
psych::describeBy(df2$Time,df2$Group)
```


## b) Type of data
```{r type_of_data}
str(defaultDf2)

df2$Group <- as.factor(df2$Group)
df2$Time <- as.numeric(df2$Time)

str(df2)

```

* The numeric type is a number that measures a value.  
* The categorical is a integer value connected to a set of characters.
* The ordinal type is a number that represents the natural order of the elements without the indication of the relative size difference.

## c) Linear Model
```{r linear_model}
lm(Time ~ Group,df2)
```

* The value for the intercept (a) is 16 according to the function. 
* The value of b is 0.01.
* The value of X is 1 for the group original and 0 for group optimized.

## d) Is the factory "Group" statistically significant for this model?
```{r ttest_group}
t.test(formula = Time~Group,
       data=df2, var.equal=T)
```

The factor group is not statistically significant since the p value is larger than the alpha value.

We can't say that time optimized is better than the original one based on our tests.


```{r qqplot_2}
timeOriginal <- df2[df2$Group == "timeOriginal",]
car::qqPlot(timeOriginal$Time, main = 'qq-Plot of perfor ', ylab= 'Time to develop')

timeOptimized <- df2[df2$Group == "timeOptimized",]
car::qqPlot(timeOptimized$Time, main = 'qq-Plot of perfor ', ylab= 'Time to develop')
```


Based on the qq-plots the data fulfills the assumptions for the linear regression model. 



